Hurricane Evacuation Strategies for the State of Mississippi

### 2015-11-16 manuscript.tex
network representation done

\section{Network Representation of Mississippi}
\label{sec:representation}
  \par
    The MSEMA specified that our plan should be enacted on a per-county basis. As you can see in the following figure, these counties are approximately equally sized. As a result of this, we assume that each county can be modeled as a single node in a bidirectional graph. Then an edge from node $i$ to node $j$ represents an available evacuation route from county $i$ to county $j$. In all of our models we assume that highways are the only means of evacuation. Therefore, we constructed a network of Mississippi counties by connecting each county's node to the nodes of all bordering counties directly reachable by highways:
  \begin{figure}[H]
    \center
    \begin{subfigure}[b]{0.5\textwidth}
      \center
      \includegraphics[width=.9\linewidth]{figures/county_map.jpg}
      \caption*{A Map of Counties in the State of Mississippi \cite{county_map}}
    \end{subfigure}~
    \begin{subfigure}[b]{0.5\textwidth}
      \center
      \includegraphics[width=\linewidth]{figures/full_undirected-crop.pdf}
      \caption*{Undirected Graph Representing Mississippi Counties}
    \end{subfigure}
    \caption*{}
  \end{figure}
  \par
     Because Mississippi has varying highway structure, it would be inappropriate to assume uniform travel rates between county pairs. In order to capture this heterogeneity in the network model, we decided to assign weights to every edge. Then a single edge weight represents a carrying capacity for the amount of travel possible between two counties. For a real-world mapping, we assume that this would correspond to the total number of highway lanes spanning two counties. Therefore, we were able to assign edge weights across the entire graph by using the following highway map:
  \begin{figure}[H]
    \centering
    \includegraphics[width=.5\textwidth]{ms_highways.pdf}
    \caption{Map of Major Highways in the State of Mississippi \cite{ms_highways}}
    \label{fig:highway_map}
  \end{figure}
  \par
    In this figure, the thick black lines represent four lane highways while the red lines represent two lane highways. We assume that despite the ensuing panic, evacuees still travel along the right side of the highway, even if this means lanes going the other way (towards the hurricane) are underutilized. Therefore, for every thick black line spanning two counties, the appropriate edge in the graph gains two additional lanes, whereas red lines add one lane. Summing the lane contributions of all highways for a pair of counties therefore gives us an single edge weight in the graph.
  \newline
  \par
    We assume that there is a fixed spacing between every car on every highway. Then all cars travel at the same speed, and the density of cars is uniform along the entire length of every highway. This determines a fixed flow rate per edge capacity, and allows us to compute the number of cars traveling to another county in a given time interval. Because of the inevitable traffic congestion during an evacuation, we set the fixed speed to a relatively slow $10$ km/hr. In a traffic jam situation like this, we expect a tight traffic density of one car every 10 meters. Therefore:
    \[
      \frac{10\ \text{km/hr}}{10\ \text{m/car}} = 1000\ \text{cars/hr}
    \]
  \par
    We assume that evacuees travel with friends and family in their cars. Because the average size of an American family is \texttildelow 3 persons \cite{famsize}, we conclude that 3000 people per hour can use a single lane to another county. Maximum population flow rates between each county are therefore three thousand times the corresponding edge weight.

>>>>

\section{Network Representation of Mississippi}
\label{sec:representation}
  \par
    The MSEMA specified that our plan should be enacted on a per-county basis. As you can see in the following figure, these counties are approximately equally sized. As a result of this, we assume that each county can be modeled as a single node in a bidirectional graph. Then an edge from node $i$ to node $j$ represents an available evacuation route from county $i$ to county $j$. In all of our models we assume that highways are the only means of evacuation. Therefore, we constructed a network of Mississippi counties by connecting each county's node to the nodes of all bordering counties directly reachable by highways:
  \begin{figure}[H]
    \center
    \begin{subfigure}[b]{0.5\textwidth}
      \center
      \includegraphics[width=.9\linewidth]{figures/county_map.jpg}
      \caption*{A Map of Counties in the State of Mississippi \cite{county_map}}
    \end{subfigure}~
    \begin{subfigure}[b]{0.5\textwidth}
      \center
      \includegraphics[width=\linewidth]{figures/full_undirected-crop.pdf}
      \caption*{Undirected Graph Representing Mississippi Counties}
    \end{subfigure}
    \caption*{}
  \end{figure}
  \par
     Because Mississippi has varying highway structure, it would be inappropriate to assume uniform travel rates between all county pairs. In order to capture this heterogeneity in the network model, we decided to assign weights to every edge. Then a single edge weight represents a carrying capacity for the maximum amount of travel between two counties. For a real-world mapping of this, we assume that this would correspond to the total number of highway lanes spanning two counties. Therefore, we were able to assign edge weights across the entire graph by using the following highway map:
  \begin{figure}[H]
    \centering
    \includegraphics[width=.5\textwidth]{ms_highways.pdf}
    \caption{Map of Major Highways in the State of Mississippi \cite{ms_highways}}
    \label{fig:highway_map}
  \end{figure}
  \par
    In this figure, the thick black lines represent four lane highways while the red lines represent two lane highways. We assume that despite the ensuing panic, evacuees still travel along the right side of the highway, even if this means lanes going the other way (towards the hurricane) are underutilized. Therefore, for every thick black line spanning two counties, the appropriate edge in the graph gains two additional lanes, whereas red lines add one lane. Summing the lane contributions of all highways for a pair of counties therefore gives us an single edge weight in the graph.
  \newline
  \par
    We assume that there is a fixed spacing between every car on every highway. Then all cars travel at the same speed, and the density of cars is uniform along the entire length of every highway. This determines a fixed flow rate per edge capacity, and allows us to compute the number of cars traveling to another county in a given time interval. Because of the inevitable traffic congestion during an evacuation, we set the fixed speed to a relatively slow $10$ km/hr. In a traffic jam situation like this, we expect a tight traffic density of one car every 10 meters. Therefore:
    \[
      \frac{10\ \text{km/hr}}{10\ \text{m/car}} = 1000\ \text{cars/hr}
    \]
  \par
    We assume that evacuees travel with friends and family in their cars. Because the average size of an American family is \texttildelow 3 persons \cite{famsize}, we conclude that 3000 people per hour can use a single lane to another county. Maximum population flow rates between each county are therefore three thousand times the corresponding edge weight.
